%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {\underline{FPT Software}} % Organisation
  {Hanoi, Vietnam} % Location
  {Apr 2021 - now} % Date(s)
  {
  	\begin{cvitems} % Description(s) of tasks/responsibilities
  		\item[ ] {\textbf {Digital Health Platform}}
  		\item {Collaborated with a scrum team to develop a health platform for a US company that utilize to build the application for the healthcare industry like hospitals, health providers, etc.}
  		\item {Tested and deployed code using Agile methodologies.}
  		\item {Maintained and improved existing codebase.}
  		\item {Participated in code reviews and contributed to improving coding standards and best practices.}
  		\item {Supported automation testing using Selenium, Appium, WebdriverIO.}
  		%\item {\textbf{Technical Skills:} Java (SpringBoot), GCP, PostgreSQL, Redis, Jmeter, ForgeRock, Bitbucket, Jenkins.}
  		%\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
  		%\item[ ]
  		\item[ ] {\textbf {Insurance Application}}
  		\item {Collaborated with a scrum team to develop a mobile insurance application for a country in the ASIA market. This app provides telehealth, vaccination reminders, rewards as coupons, etc.}
  		\item {Improved APIs performance.}
  		\item {Support automation testing using Selenium, Appium, WebdriverIO.}
  		\item[ ]
  		%\item {\textbf{Technical Skills:} Java (SpringBoot), Azure, Jmeter,  Bitbucket, Jenkins.}
  		%\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
  	\end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {\underline{Viettel Business Solutions}} % Organisation
  {Hanoi, Vietnam} % Location
  {Oct 2020 - Apr 2021} % Date(s)
  {
  	\begin{cvitems} % Description(s) of tasks/responsibilities
  		\item[ ] {\textbf {Government Project}}
  		\item {Worked as a Team Leader for government projects.}
  		\item {Manage resources to develop, maintain and customize some government application.}
  		\item {Improved application performance, Fixing the security bugs.}
  		\item {Participated in code reviews and contributed to improving coding standards and best practices.}
  		\item {Worked closely with clients to understand their requirements and provide technical solutions.}
  		\item[ ]
  		%\item {\textbf{Technical Skills:} Java Spring Boot, Liferay, MySQL, Oracle, Unix.}
  		%\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
  	\end{cvitems}
  }
  
  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {\underline{FPT Software}} % Organisation
  {Hanoi, Vietnam} % Location
  {Oct 2017 - Oct 2020} % Date(s)
  {
  	\begin{cvitems} % Description(s) of tasks/responsibilities
  		\item[ ] {\textbf {Logistic Project}}
  		\item {Worked as a Team Leader after 1.5 years. Responsible for customizing a core supply chain system of the EU branch of Japan company. The application's key are: Basic Supply Chain Management (SCM) business processes are standardized GloballyProduction, Sales, and Inventory (PSI) related information is consolidated for cross-regional visualization and real-time data communication. Basic SCM Masters are consolidated globally, enabling consistent and accurate information to management.}
  		\item {Developed and maintained Java-based web applications for clients in the US and UK.}
		\item {Synced information from third-party via message queue, SOAP.}
  		\item {Involved in analysis and design system.}
  		\item {Improved performance for the web application.}
  		%\item {\textbf{Technical Skills:} Java 6, EJB 2. x, Strust 2. x, Oracle database, PL/SQL, Jenkins, Git.}
  		%\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
  	\end{cvitems}
  }

\end{cventries}
